P. berghei pir - Sample clustering/PCA

### 2021-12-03 chapter3_results_bergheiPir/Pberghei_pir_samples_hclust-PCA-topGenes.Rmd
Reverse previous changes, need to save name of experiment in expt_tpms object

```{r read_tpm}
berghei_tpm <- read.csv('berghei_tpm.csv', 
                        row.names = 1)
```

>>>>

```{r read_tpm}
berghei_tpm <- read.csv('berghei_tpm.csv', 
                        row.names = 1)
expt_tpms <- lapply(na.omit(unique(str_extract(colnames(berghei_tpm), pattern = 'E[[:digit:]]{2}'))),
                    function(Enum){
                      df <- berghei_tpm[,str_subset(colnames(berghei_tpm), 
                                              pattern = paste0('Geneid|',Enum))]
                      list(experiment = Enum,
                           tpm = df)
                    })
names(expt_tpms) <- na.omit(unique(str_extract(colnames(berghei_tpm), pattern = 'E[[:digit:]]{2}')))
```
